Conservation decision-making under long transients

### 2019-08-06 slides/boettiger.Rmd
WIP

## Dynamics from the deterministic skeleton

@@

---
background-image: linear-gradient(to right, rgba(50, 50, 50, .8), rgba(50, 50, 50, .95)), url(img/royalsociety/gentoo-penguin.jpg)
background-size: 120%
class: center, top, inverse
background-position: center

@@

---
background-image: linear-gradient(to right, rgba(50, 50, 50, .8), rgba(50, 50, 50, .95)), url(img/royalsociety/gentoo-penguin-wtf.jpg)
background-size: 120%
class: center, top, inverse
background-position: center

@@

---
background-image: linear-gradient(to right, rgba(50, 50, 50, .6), rgba(50, 50, 50, .9)), url(img/royalsociety/snake.jpg)
background-size: 120%
class: center, top, inverse
background-position: center

@@

---
background-image: linear-gradient(to right, rgba(50, 50, 50, .6), rgba(50, 50, 50, .9)), url(img/royalsociety/reef-shark.jpg)
background-size: 120%
class: center, top, inverse

>>>>

## Time-series of the dynamics from the deterministic skeleton

@@

---
background-image: linear-gradient(to right, rgba(50, 50, 50, .7), rgba(50, 50, 50, .95)), url(img/royalsociety/gentoo-penguin.jpg)
background-size: 110%
class: center, top, inverse
background-position: center

@@

---
background-image: linear-gradient(to right, rgba(50, 50, 50, .7), rgba(50, 50, 50, .95)), url(img/royalsociety/gentoo-penguin-wtf.jpg)
background-size: 110%
class: center, top, inverse
background-position: center

@@

---
background-image: linear-gradient(to right, rgba(50, 50, 50, .7), rgba(50, 50, 50, .95)), url(img/royalsociety/gentoo-penguin.jpg)
background-size: 110%
class: center, top, inverse
background-position: center

#  First-passage times to the stable attractor

```{r echo=FALSE}
## det equib
# data  %>% filter(t == max(t)) %>% pull(x) %>% mean() ## ~ 1.25

## First-passage time, tau
passage <- data %>% group_by(reps) %>% filter(x > 1.25) %>% summarise(tau = min(t))
det_tau <- det %>% group_by(reps) %>% filter(x > 1.25) %>% summarise(tau = min(t)) %>% pull(tau)

passage %>% ggplot(aes(tau)) + geom_histogram(binwidth = 200, fill=rgb(.95,.95,.95)) + geom_vline(aes(xintercept=det_tau), col="blue", lwd=2) #+ theme_bw(42)

---
background-image: linear-gradient(to right, rgba(50, 50, 50, .7), rgba(50, 50, 50, .95)), url(img/royalsociety/gentoo-penguin.jpg)
background-size: 110%
class: left, top, inverse
background-position: center

# Features that drive long transient dynamics also create stochastic phenomena

- Emergent ensemble dynamics not predicted by the deterministic model
- ... But intuition is simple: noise helps 'jump' the ghost
- .... But also creates dynamics that are deeply challenging for both inference & decision-making

---
background-image: linear-gradient(to right, rgba(50, 50, 50, .8), rgba(50, 50, 50, .95)), url(img/royalsociety/reef-shark.jpg)
background-size: 120%
class: center, top, inverse
background-position: center

@@

---
background-image: linear-gradient(to right, rgba(50, 50, 50, .8), rgba(50, 50, 50, .95)), url(img/royalsociety/reef-shark.jpg)
background-size: 120%
class: left, top, inverse

Given time-series observations, can
